%--------------------------------------------------
% CV in LaTeX
% Author  : Joyant Sheikhar Gupta Joy
% Based on: https://github.com/joyant-s-g-j
% License : MIT
%--------------------------------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{tabularx}
\usepackage{mathptmx}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\footskip}{10pt}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\rmfamily\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSection}[2]{
  \section{\textbf{\href{#1}{#2}}}
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabularx}{\textwidth}[t]{X r}
      \textbf{#1} & #2 \\
      \textbf{\textit{\href{#3}{\small #4}}} & \textit{\small #5} \\
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeEduSubheading}[6]{
  \vspace{-2pt}\item
    \begin{tabularx}{\textwidth}[t]{X r}
      \textbf{\href{#1}{#2}} & #3 \\
      {\textit{\small #4}} & \textit{\small #5} \\
      {\small #6}
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeCourseheading}[1]{
  \vspace{-2pt}\item
    \textbf{#1}\vspace{-7pt} \\
}

\newcommand{\resumeCoursework}[1]{
  \vspace{2pt}
  \begin{multicols}{3}
    \begin{itemize}[leftmargin=*, label=\textbullet, itemsep=2pt]
      #1
    \end{itemize}
  \end{multicols}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabularx}{\textwidth}{X r}
      #1 & #2 \\
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
{\Huge \rmfamily Joyant Sheikhar Gupta Joy} \\ \vspace{1pt}
\small \textbf{Software Developer $|$ CSE Student at \href{https://www.adust.edu.bd/}{ADUST}} \\ \vspace{2pt}
\href{tel:+8801518683509}{\underline{+8801518683509}} $|$ 
\href{mailto:joyantsheikharguptajoy@gmail.com}{\underline{joyantsheikharguptajoy@gmail.com}} $|$ 
Dhaka, Bangladesh \\ \vspace{1pt}
\href{https://www.joyantsgj.dev/}{\underline{www.joyantsgj.dev}} $|$
\href{https://www.linkedin.com/in/joyant-s-g-j/}{\underline{linkedin.com/in/joyant-s-g-j}} $|$
\href{https://github.com/joyant-s-g-j}{\underline{github.com/joyant-s-g-j}}

%----------Professional Summary----------
\resumeSection{https://www.joyantsgj.dev/about}{About Me}
    A Computer Science \& Engineering student focused on full-stack development and problem-solving, with practical experience in building web applications. Passionate about technology, continuous learning, and exploring fields like Machine Learning. Actively contributes to collaborative projects with a goal of creating real-world solutions.
%-----------EDUCATION-----------
\resumeSection{https://www.joyantsgj.dev/education}{Education}
  \resumeSubHeadingListStart
    \resumeEduSubheading
        {https://www.adust.edu.bd/\#}{Atish Dipankar University of Science and Technology}{Dhaka, Bangladesh}
        {Bachelor of Science in Computer Science and Engineering }{Jan 2024 -- Dec 2027 (Expected)}
        {Up to 6th semester CGPA: 3.50}
    \resumeCourseheading{Relevant Coursework}
        \resumeCoursework{
            \item Data Structures
            \item OOP (Java)
            \item Algorithms
            \item Discrete Mathematics
            \item Computer Architecture
            \item Data Communication
            \item Software Engineering
            \item Operating Systems
            \item Computer Networking
        }
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\resumeSection{https://www.joyantsgj.dev/skills}{Skills}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
        \textbf{Languages}{: C, C++, Java, JavaScript, TypeScript, Python, SQL, LaTeX} \\
        \textbf{Concepts}{: Problem-Solving, Competitive Programming, Data Structures, Algorithms, OOP} \\
        \textbf{Frontend}{: HTML, CSS, Chakra UI, JavaScript, React (MERN), Next.js, Tailwind, Bootstrap} \\
        \textbf{Backend}{: Django, Express.js, Node.js (MERN)} \\
        \textbf{Mobile Development}{: React Native} \\
        \textbf{Machine Learning}{: Scikit-learn, Pandas, NumPy, Matplotlib, Seaborn, Plotly} \\
        \textbf{Database}{: MySQL, PostgreSQL, MongoDB} \\
        \textbf{Tools}{: Git, GitHub, Figma, GitBook, Notion, VS Code} \\
        \textbf{Operating Systems}{: Windows, Linux (Ubuntu)} \\
        \textbf{Soft Skills}{: Communication, Collaboration, Adaptability, Leadership, Time Management, Flexibility, Decision-Making}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\resumeSection{https://www.joyantsgj.dev/experience}{Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Software Developer Intern}{May 2025 -- September 2025}
            {https://www.thinkcrypt.dev/}{Thinkcrypt.io}{Banani, Dhaka, Bangladesh }
        \resumeItemListStart
            \resumeItem{Built 6+ full-stack projects using the MERN stack with scalable APIs and responsive UIs; currently working on more.}
            \resumeItem{Developed frontend interfaces using Next.js, Chakra UI, and Tailwind CSS; managed state with Redux Toolkit.}
            \resumeItem{Collaborated in a 4-member team to fix bugs, enhance performance, and deliver core product features.}
            \resumeItem{Maintained efficient version control and team collaboration using Git and GitHub.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\resumeSection{https://www.joyantsgj.dev/projects}{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{\href{https://github.com/joyant-s-g-j/Abashon-App}{Abashon}} $|$ \emph{React Native, Expo, Node.js, Express.js, MongoDB, Socket.IO, Stripe}}{September 2025 -- January 2026}
    \resumeItemListStart
      \resumeItem{Built a full-stack real estate mobile app with property listings, advanced search/filtering, and favorites functionality.}
      \resumeItem{Implemented JWT \& Google OAuth authentication with role-based access control and admin dashboard.}
      \resumeItem{Developed real-time messaging system using Socket.IO with image/video sharing and Cloudinary storage.}
      \resumeItem{Integrated Stripe payment gateway for property bookings and Google Maps for location visualization.}
      \resumeItem{Designed responsive UI with NativeWind (TailwindCSS) featuring custom fonts and dark/light property cards.}
    \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{\href{https://huggingface.co/spaces/joyant-s-g-j/Diabetes-Predictor}{Diabetes Predictor}} $|$ \emph{Python, Scikit-learn, Pandas, NumPy, Gradio}}{January 2026 -- February 2026}
    \resumeItemListStart
      \resumeItem{Built an ML web app predicting diabetes using Random Forest Classifier with probability scores.}
      \resumeItem{Implemented preprocessing pipeline with outlier detection, StandardScaler, and OneHotEncoder.}
      \resumeItem{Engineered health risk feature combining hypertension and heart disease for improved accuracy.}
      \resumeItem{Deployed interactive Gradio interface on Hugging Face Spaces for real-time predictions.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{\textbf{Certifications}}
  \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
      \textbf{Front-end Development – Sheriyans Coding School}{: Covered HTML, CSS, JavaScript, GSAP, Locomotive, Scroll Trigger, Shery.js, React.js, Tailwind, Redux, and modern web development principles.} \\
      \textbf{Python (Basic) – HackerRank}{: Validated foundational Python skills, including data types, control structures, functions, and problem-solving.}
    }}
  \end{itemize}

%-----------Publications \& Science Writing-----------
\section{\textbf{Publications \& Science Writing}}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Editor-in-Chief and Science Article Writer}{Jan 2023 -- Jan 2025}
            {https://bangachi.com/}{Bangachi}{Virtual Platform}
        \resumeItemListStart
            \resumeItem{Joyant led the content team at Bangachi, an online science platform for young learners in Bangladesh.}
            \resumeItem{He wrote and translated articles to explain science topics in simple Bengali.}
            \resumeItem{He edited books like \textbf{\textit{Mini Monsters}, \textit{Ei Boita Sci-Fi Er}} \& \textbf{\textit{Savanar Sat}}.}
            \resumeItem{Through this role, he helped make science fun, clear, and interesting for a wide audience.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Extracurricular Activities \& Interests-----------
\section{\textbf{Extracurricular Activities \& Interests}}
    \small
    Joyant has completed a 10km marathon and plans to participate in more events in the future. He enjoys photography, adventure traveling, and writing travel stories. He writes on various science topics aiming to make them simple and interesting, and also writes creatively about romanticism as a personal interest. In his free time, he solves Rubik’s Cubes, plays chess, and reads science books.

%-----------LEADERSHIP AND VOLUNTEER-----------
\section{\textbf{Leadership \& Volunteer Experience}}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Campus Ambassador}{May 2025 -- November 2025}
            {https://phitron.io/}{Phitron}{Virtual Platform}
        \resumeItemListStart
            \resumeItem{Joyant was selected as the official Campus Ambassador for his university under a 6-month leadership program.}
            \resumeItem{He promoted tech education, organized campus activities, and helped build a strong learning community.}
            \resumeItem{He regularly joined tech and career upskilling sessions and connected with industry professionals.}
            \resumeItem{He also supported Phitron’s branding on LinkedIn and got access to special certifications and job opportunities.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------LANGUAGES-----------
\section{\textbf{Languages}}
  \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
      \textbf{Bangla}{: Native} \\
      \textbf{English}{: Professional working proficiency} \\
      \textbf{Hindi}{: Good reading and speaking skills}
    }}
  \end{itemize}

%-----------References-----------
\section{\textbf{References}}
    \begin{itemize}[leftmargin=0in, label={}]
    \item \small{
        \textbf{Nayeem Hossain Faruque} \\
        Database Administrator, Dohatec New Media \\
        Email:  \href{mailto:nayeemhossainfaruque@gmail.com}{nayeemhossainfaruque@gmail.com} \\
        LinkedIn:  \href{https://www.linkedin.com/in/nayeem-hossain-faruque-4a3865294/}{linkedin.com/in/nayeem-hossain-faruque}\\
    }
    \vspace{5pt}
    \item \small{
        \textbf{Anup Saha} \\
        Business Analytics, APIE \\
        Email:  \href{mailto:anupsahabd1971@gmail.com}{anupsahabd1971@gmail.com}\\
        LinkedIn: \href{https://www.linkedin.com/in/anup-saha-31589816a/}{linkedin.com/in/anup-saha} \\
    }
    \end{itemize}

\end{document}